---
title: "ITP Simulation"
author: "Chase Latour"
date: "6/22/2020"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Objective

Save the figures generated in the ITP simulation analyses.


```{r include=FALSE}

# Load packages that need

# Installed packages
#renv::install(c("tidyr","purrr","knitr"))

# Call necessary packages
library(purrr)
library(furrr)
future::plan("sequential")
# Alex recommends 'multisession' - Run as 'sequential' when on the test.stat server.
library(dplyr) 
library(tidyr)
library(ggplot2)
library(knitr)
library(kableExtra)

```


# Load in Datasets

Load in the already-simulated datasets that we need for the additional largest difference analysis.

```{r}

# N = 200

B1 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/B1_all_corr_morePS.rds")

B2 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/B2_all_corr_morePS.rds")

B3 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/B3_all_corr_morePS.rds")

B4 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/B4_all_corr_morePS.rds")

RB1 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/RB1_all_corr_morePS.rds")

RB3 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/RB3_all_corr_morePS.rds")

# # N = 1,000
# 
# A1 <- readRDS("~/projects/P0047/users/clatour/plans/Simulated R Data/A1_all_corr.rds")
# 
# A2 <- readRDS("~/projects/P0047/users/clatour/plans/Simulated R Data/A2_all_corr.rds")
# 
# A3 <- readRDS("~/projects/P0047/users/clatour/plans/Simulated R Data/A3_all_corr.rds")
# 
# A4 <- readRDS("~/projects/P0047/users/clatour/plans/Simulated R Data/A4_all_corr.rds")
# 
# RA1 <- readRDS("~/projects/P0047/users/clatour/plans/Simulated R Data/AB1_all_corr.rds")
# 
# RA3 <- readRDS("~/projects/P0047/users/clatour/plans/Simulated R Data/AB3_all_corr.rds")

```

# Plot Median Differences

Use the previous function to plot the median differences across all 2,000 simulations for each scenario.

## Function

The code below prints a violin plot for the median difference in platelet counts over the simulations.

```{r}

graph_md_dots <- function(dat, effect = 0, title, subtitle){
  
  # Gather the datset to be long, with the minimum number of variables so that it can be plotted
  plot <- dat %>% 
  select(sim_id,  md_PSgold, md_PSmean, md_PSsd, md_PSrdiff, md_PSlargest, md_mean_sd, md_all) %>% 
  pivot_longer(cols = c(md_PSgold, md_PSmean, md_PSsd, md_PSrdiff, md_PSlargest, md_mean_sd, md_all), 
               names_to = "PS_adj", values_to = "estimate")
  
  plot2 <- plot %>% 
  ggplot(aes(x = PS_adj, y = as.integer(estimate))) +
    geom_violin(trim = FALSE) +
    geom_hline(yintercept = effect, linetype = "dashed", color = "red") +
    labs(title = paste0("Median Difference Estimate by Adjustment Method for ",
                        title), 
         subtitle = paste0(subtitle),
         x = "Adjustment Method", 
         y = "Median Difference of Platelet Counts") +
    scale_x_discrete(
      limits=c("md_PSmean", "md_PSsd", "md_PSrdiff",
                "md_PSlargest", "md_mean_sd", "md_all","md_PSgold"),
      labels=c("Mean", "Standard Dev", "Most Recent", "Largest", "Mean and SD", "All",
               "ITP Strata")
      ) +
    geom_jitter(width = 0.1, size = 0.25) +
    theme_bw()
  
    ggsave(filename = paste(title, "with dots_morePS.jpeg"),
         plot = plot2,
         path = "~/projects/P0047/users/chase.latour/plans/Figures/",
         units = "in",
         width = 7,
         height = 5)
    
    return(plot2)
    
} 



graph_md_nodots <- function(dat, effect = 0, title, subtitle){
  
  # Gather the datset to be long, with the minimum number of variables so that it can be plotted
  plot <- dat %>% 
  select(sim_id, md_PSmean, md_PSsd, md_PSrdiff, md_PSlargest, md_PSgold, md_mean_sd, md_all) %>% 
  pivot_longer(cols = c(md_PSmean, md_PSsd, md_PSrdiff, md_PSlargest, md_PSgold, md_mean_sd, md_all), 
               names_to = "PS_adj", values_to = "estimate")
  
  plot2 <- plot %>% 
  ggplot(aes(x = PS_adj, y = as.integer(estimate))) +
    geom_violin(trim = FALSE) +
    geom_hline(yintercept = effect, linetype = "dashed", color = "gray") +
    labs(title = paste0("Median Difference Estimates for ",
                        title), 
         x = element_blank(), 
         y = "Median Difference",
         caption = "The star indicates the median of the differences between the two treatment groups' median follow-up platelet counts.") +
    scale_x_discrete(
      limits=c("md_PSmean", "md_PSsd", "md_PSrdiff",
                "md_PSlargest", "md_mean_sd", "md_all","md_PSgold"),
      labels=c("Mean", "Standard Dev", "Most Recent", "Largest", "Mean and SD", "All",
               "Gold Standard"),
      
      ) +
    scale_y_continuous(limits = c(-50,15)) +
    #geom_jitter(width = 0.1, size = 1) +
    theme_bw() +
    theme(axis.text.x = element_text(size=rel(1.35), colour = 'black'),
          axis.text.y = element_text(size = rel(1.15), colour = 'black')) +
    ggplot2::stat_summary(fun = median, geom = "point", color = 'black',
                          size = 1.25, shape = 8)
  
  ggsave(filename = paste(title, "without dots_morePS.jpeg"),
         plot = plot2,
         path = "~/projects/P0047/users/chase.latour/plans/Figures/",
         units = "in",
         width = 7,
         height = 5)
  
  return(plot2)
}

# Look here for info on editing tick marks: https://www.datanovia.com/en/blog/ggplot-axis-ticks-set-and-rotate-text-labels/

```

## Scenario B1

* Number of participants in initial cohort (N): 200

* More Severe ITP: $\mu = 40 \text{, } \sigma = 15$

  + Probability of SOC = 0.4; Probability of ROM = 0.6
  
* Less Severe ITP: $\mu = 100 \text{, } \sigma = 50$

  + Probability of SOC = 0.6; Probability of ROM = 0.4

### Null Effect

```{r}

#graph_md_dots(B1, title = "Scenario B1")

graph_md_nodots(B1, title = "Scenario B1")

```


## Scenario B2

* Number of participants in initial cohort (N): 200

* More Severe ITP: $\mu = 40 \text{, } \sigma = 15$

  + Probability of SOC = 0.2; Probability of ROM = 0.8
  
* Less Severe ITP: $\mu = 100 \text{, } \sigma = 50$

  + Probability of SOC = 0.8; Probability of ROM = 0.2
  
### Null Effect

```{r}

#graph_md_dots(B2, title = "Scenario B2")

graph_md_nodots(B2, title = "Scenario B2")

```


## Scenario B3

* Number of participants in initial cohort (N): 200

* More Severe ITP: $\mu = 35 \text{, } \sigma = 10$

  + Probability of SOC = 0.4; Probability of ROM = 0.6
  
* Less Severe ITP: $\mu = 55 \text{, } \sigma = 20$

  + Probability of SOC = 0.6; Probability of ROM = 0.4
  
### Null Effect

```{r}

#graph_md_dots(B3, title = "Scenario B3")

graph_md_nodots(B3, title = "Scenario B3")

```


## Scenario B4

* Number of participants in initial cohort (N): 200

* More Severe ITP: $\mu = 35 \text{, } \sigma = 10$

  + Probability of SOC = 0.2; Probability of ROM = 0.8
  
* Less Severe ITP: $\mu = 55 \text{, } \sigma = 20$

  + Probability of SOC = 0.8; Probability of ROM = 0.2
  
### Null Effect

```{r}

#graph_md_dots(B4, title = "Scenario B4")

graph_md_nodots(B4, title = "Scenario B4")

```


## Scenario RB1

* Number of participants in initial cohort (N): 200

* More Severe ITP: $\mu = 40 \text{, } \sigma = 15$

  + Probability of SOC = 0.5; Probability of ROM = 0.5
  
* Less Severe ITP: $\mu = 100 \text{, } \sigma = 50$

  + Probability of SOC = 0.5; Probability of ROM = 0.5

### Null Effect

```{r}

#graph_md_dots(RB1, title = "Scenario B5")

graph_md_nodots(RB1, title = "Scenario B5")

```


## Scenario RB3

* Number of participants in initial cohort (N): 200

* More Severe ITP: $\mu = 35 \text{, } \sigma = 10$

  + Probability of SOC = 0.5; Probability of ROM = 0.5
  
* Less Severe ITP: $\mu = 55 \text{, } \sigma = 20$

  + Probability of SOC = 0.5; Probability of ROM = 0.5
  
### Null Effect

```{r}

#graph_md_dots(RB3, title = "Scenario B6")

graph_md_nodots(RB3, title = "Scenario B6")

```



**ALL THE SCENARIO A'S RIGHT NOW ARE WRITTEN FOR THE ICPE PRESENTATION SLIDES, NOT FOR THE MANUSCRIPT**

## Scenario A1

* Number of participants in initial cohort (N): 1,000

* More Severe ITP: $\mu = 40 \text{, } \sigma = 15$

  + Probability of SOC = 0.4; Probability of ROM = 0.6
  
* Less Severe ITP: $\mu = 100 \text{, } \sigma = 50$

  + Probability of SOC = 0.6; Probability of ROM = 0.4

### Null Effect

```{r eval=FALSE}

#graph_md_dots(A1, title = "Scenario A1")

graph_md_nodots(A1, title = "Scenario 2A", 
                subtitle = "Weakly Differential, Platelet Count Distributions Disparate")

```


## Scenario A2

* Number of participants in initial cohort (N): 1,000

* More Severe ITP: $\mu = 40 \text{, } \sigma = 15$

  + Probability of SOC = 0.2; Probability of ROM = 0.8
  
* Less Severe ITP: $\mu = 100 \text{, } \sigma = 50$

  + Probability of SOC = 0.8; Probability of ROM = 0.2
  
### Null Effect

```{r eval=FALSE}

#graph_md_dots(A2, title = "Scenario A2")

graph_md_nodots(A2, title = "Scenario A2")

```


## Scenario A3

* Number of participants in initial cohort (N): 200

* More Severe ITP: $\mu = 35 \text{, } \sigma = 10$

  + Probability of SOC = 0.4; Probability of ROM = 0.6
  
* Less Severe ITP: $\mu = 55 \text{, } \sigma = 20$

  + Probability of SOC = 0.6; Probability of ROM = 0.4
  
### Null Effect

```{r eval=FALSE}

#graph_md_dots(A3, title = "Scenario A3")

graph_md_nodots(A3, title = "Scenario A3")

```


## Scenario A4

* Number of participants in initial cohort (N): 1,000

* More Severe ITP: $\mu = 35 \text{, } \sigma = 10$

  + Probability of SOC = 0.2; Probability of ROM = 0.8
  
* Less Severe ITP: $\mu = 55 \text{, } \sigma = 20$

  + Probability of SOC = 0.8; Probability of ROM = 0.2
  
### Null Effect

```{r eval=FALSE}

#graph_md_dots(A4, title = "Scenario A4")

graph_md_nodots(A4, title = "Scenario A4")

```


## Scenario RA1

* Number of participants in initial cohort (N): 1,000

* More Severe ITP: $\mu = 40 \text{, } \sigma = 15$

  + Probability of SOC = 0.5; Probability of ROM = 0.5
  
* Less Severe ITP: $\mu = 100 \text{, } \sigma = 50$

  + Probability of SOC = 0.5; Probability of ROM = 0.5

### Null Effect

```{r eval=FALSE}

graph_md_dots(RA1, title = "Scenario A5")

graph_md_nodots(RA1, title = "Scenario A5")

```


## Scenario RA3

* Number of participants in initial cohort (N): 1,000

* More Severe ITP: $\mu = 35 \text{, } \sigma = 10$

  + Probability of SOC = 0.5; Probability of ROM = 0.5
  
* Less Severe ITP: $\mu = 55 \text{, } \sigma = 20$

  + Probability of SOC = 0.5; Probability of ROM = 0.5
  
### Null Effect

```{r eval=FALSE}

#graph_md_dots(RA3, title = "Scenario A6")

graph_md_nodots(RA3, title = "Scenario A6")

```

