---
title: "ITP Simulation"
author: "Chase Latour"
date: "2/9/2022"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Objective

This document summarizes patient counts for summarizing simulation performance. This is the 3rd file that is run on all of the generated data.

```{r include=FALSE}

# Load packages that need
library(tidyr)
library(dplyr)
library(kableExtra)

```

# Load in the Datasets

We have to load in the simulated data that we need.

```{r}

## Null effect

# N=10,000

A1 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/A1_all_corr_morePS.rds")

A2 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/A2_all_corr_morePS.rds")

A3 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/A3_all_corr_morePS.rds")

A4 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/A4_all_corr_morePS.rds")

RA1 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/RA1_all_corr_morePS.rds")

RA3 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/RA3_all_corr_morePS.rds")

# N=200

B1 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/B1_all_corr_morePS.rds")

B2 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/B2_all_corr_morePS.rds")

B3 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/B3_all_corr_morePS.rds")

B4 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/B4_all_corr_morePS.rds")

RB1 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/RB1_all_corr_morePS.rds")

RB3 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/RB3_all_corr_morePS.rds")



## Non-Null effect

# N=10,000

A1_50 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/A1_all50_corr_morePS.rds")

A2_50 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/A2_all50_corr_morePS.rds")

A3_50 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/A3_all50_corr_morePS.rds")

A4_50 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/A4_all50_corr_morePS.rds")

RA1_50 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/RA1_all50_corr_morePS.rds")

RA3_50 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/RA3_all50_corr_morePS.rds")


# N=200

B1_50 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/B1_all50_corr_morePS.rds")

B2_50 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/B2_all50_corr_morePS.rds")

B3_50 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/B3_all50_corr_morePS.rds")

B4_50 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/B4_all50_corr_morePS.rds")

RB1_50 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/RB1_all50_corr_morePS.rds")

RB3_50 <- readRDS("~/projects/P0047/users/chase.latour/plans/Simulated R Data/RB3_all50_corr_morePS.rds")

```

# Function to Summarize the Data

Write functions that will summarize patient counts.

```{r}

# Create the function that actually creates the variables.
summarize_n <- function(dataset){
  
  # Use the summarize function to calculate the stats of-interest based off the nested data tibble
  # This will return a tibble that will be inserted as a column into the dataset
  data1 <- dataset %>%
    ungroup %>% 
    summarize(n_rom_sev = sum(treatment == "ROM" & severity_n == 1),
              n_soc_sev = sum(treatment == "SOC" & severity_n == 1),
              n_sev = sum(severity_n == 1),
              n_rom_nsev = sum(treatment == "ROM" & severity_n == 0),
              n_soc_nsev = sum(treatment == "SOC" & severity_n == 0),
              n_nsev = sum(severity_n == 0))
  
  return(data1)

  
}

## Apply

summary <- function(dataset){
  
  # Apply the above function to the dataset that you're summarizing
  data1 <- dataset %>% 
    # Select only those variables that we need (more efficient)
    select(sim_id, data) %>% 
    # Calculate the summary tibble
    mutate(n_summary = purrr::map(data, ~summarize_n(.x))) %>% 
    # Remove the data that donn't need
    select(-data) %>% 
    # Unnest the dataset so that each summary stat is a column.
    # This will give 1 row per simulation
    unnest(cols = n_summary)
  
  # Calculate the median and IQRs of these new measures
  data2 <- data1 %>% 
    ungroup() %>% 
    summarize(p50_rom_sev = round(median(n_rom_sev), 2), # Trt with rom and more severe
              p25_rom_sev = round(quantile(n_rom_sev, 0.25), 2),
              p75_rom_sev = round(quantile(n_rom_sev, 0.75), 2),
              p50_soc_sev = round(median(n_soc_sev), 2), # Trt with SOC and more severe
              p25_soc_sev = round(quantile(n_soc_sev, 0.25), 2),
              p75_soc_sev = round(quantile(n_soc_sev, 0.75), 2),
              p50_sev = round(median(n_sev), 2), # Number of more-severe
              p25_sev = round(quantile(n_sev, 0.25), 2),
              p75_sev = round(quantile(n_sev, 0.75), 2),
              p50_rom_nsev = round(median(n_rom_nsev), 2), # Trt with rom and less severe
              p25_rom_nsev = round(quantile(n_rom_nsev, 0.25), 2),
              p75_rom_nsev = round(quantile(n_rom_nsev, 0.75), 2),
              p50_soc_nsev = round(median(n_soc_nsev), 2), # Trt with SOC and less severe
              p25_soc_nsev = round(quantile(n_soc_nsev, 0.25), 2),
              p75_soc_nsev = round(quantile(n_soc_nsev, 0.75), 2),
              p50_nsev = round(median(n_nsev), 2), # Number of less-severe
              p25_nsev = round(quantile(n_nsev, 0.25), 2),
              p75_nsev = round(quantile(n_nsev, 0.75), 2)) %>% 
    # Format the IQRs the way that will be able to be visualized.
    mutate(iqr_rom_severe = paste(p25_rom_sev, p75_rom_sev, sep = ", "),
           iqr_soc_severe = paste(p25_soc_sev, p75_soc_sev, sep = ", "),
           iqr_severe = paste(p25_sev, p75_sev, sep = ", "),
           iqr_rom_nsevere = paste(p25_rom_nsev, p75_rom_nsev, sep = ", "),
           iqr_soc_nsevere = paste(p25_soc_nsev, p75_soc_nsev, sep = ", "),
           iqr_nsevere = paste(p25_nsev, p75_nsev, sep = ", ")) %>% 
    # Select only those variables that want to put in a kable function
    select(p50_rom_sev, iqr_rom_severe, p50_soc_sev, iqr_soc_severe, p50_sev, iqr_severe,
           p50_rom_nsev, iqr_rom_nsevere, p50_soc_nsev, iqr_soc_nsevere, p50_nsev, iqr_nsevere)
  
  # Use the kable function to build a table that is nice to review
  kabletable <- kable(data2,
                      col.names = c("Median", "IQR", "Median", "IQR", "Median", "IQR",
                                    "Median", "IQR", "Median", "IQR", "Median", "IQR"),
                      align = "c") %>% 
    kable_classic() %>% 
    add_header_above(c("N More Severe Romi" = 2,
                       "N More Severe SOC" = 2,
                       "N More Severe" = 2,
                       "N Less Severe Romi" = 2,
                       "N Less Severe SOC" = 2,
                       "N Less Severe" = 2))
  
  # Return that kable table at the end of the run.
  return(kabletable)
  
}

```

# Print out the tables

These are only printed for null treatment effects because they are the exact same regardless of effect size. It is only summarizing the N in each cell, which is determined prior to adding the treatment effect.

```{r}

## N = 200

summary(B1)

summary(B2)

summary(B3)

summary(B4)

summary(RB1) # B5

summary(RB3) # B6

## N = 10,000

summary(A1)

summary(A2)

summary(A3)

summary(A4)

summary(RA1) # B5

summary(RA3) # B6

```